---
title: "Synthetic Sales Analysis - R Script Documentation"
author: "ALI BEHESHTINEJAD"
date: "September 28, 2026"
output: html_document
---

**AI Assistance Declaration:** I used ChatGPT (GPT-5.6 Sol) for documentation structure, Markdown drafting, wording refinement, and formatting suggestions. Prompts used are listed in `Appendix_AI.md`. I verified outputs by reviewing the Markdown structure, previewing the README on GitHub, and knitting the R Markdown file in Posit Cloud. All final calculations are done by myself. No real or personal data were uploaded. I am responsible for the accuracy and originality of this work.

# Purpose

This document explains a small R workflow that uses a synthetic sales dataset. Its purpose is to demonstrate clear R Markdown documentation with organized sections, explanatory text, and syntax-highlighted R code chunks.

# Inputs

The example uses synthetic monthly sales information created directly in R. No real or personal information is used.

The input contains two fields:

- `month`: a month label.
- `revenue`: a synthetic monthly revenue value.

# Dependencies

The example uses the `ggplot2` package for visualization.

```{r setup, message=FALSE}
library(ggplot2)
```

# Create the Synthetic Data

```{r create-data}
sales <- data.frame(
  month = c("Jan", "Feb", "Mar", "Apr", "May", "Jun"),
  revenue = c(12000, 13500, 12800, 15100, 16000, 17200)
)
```

# Inspect the Data

The following code displays the structure and first rows of the synthetic dataset.

```{r inspect-data}
str(sales)
head(sales)
```

# Summarize the Data

The following code asks R to summarize the synthetic revenue variable.

```{r summarize-data}
summary(sales$revenue)
```

# Visualize the Data

```{r visualize-data}
ggplot(sales, aes(x = month, y = revenue)) +
  geom_col() +
  labs(
    title = "Synthetic Monthly Revenue",
    x = "Month",
    y = "Revenue"
  )
```

# Outputs

When this R Markdown file is knitted, it produces:

- A displayed description of the synthetic dataset.
- A preview of the dataset.
- Summary statistics for the `revenue` field.
- A bar chart of monthly synthetic revenue.

# Validation

This `.Rmd` file was successfully knitted in Posit Cloud. The rendered document was reviewed to confirm that the headings, sections, R code chunks, output, and chart display correctly. Only synthetic data are used.

# AI Use Note

AI was used for documentation structure, Markdown organization, wording refinement, and code-block formatting suggestions. The prompts and key response summaries are documented in `Appendix_AI.md`.
